A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-02-21 sections/methodology/main.tex
Change vocabulary in methodology section

The problem defined in section \ref{sec:model_overview} describes a normal-form
game between the decision makers of two queueing systems and a third player that 
decides how to distribute individuals to the systems.
The strategy space of the two queueing systems is defined as the possible values
that the threshold parameter can take \(T_i \in [1, N_i]\).
Then, the distributor has to decide on the proportion of individuals to send to 
each queueing system \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
and \(p_A + p_B = 1\).
Figure \ref{fig:imperfect_info_game} 
shows a diagrammatic representation of the game to be played and the decisions 
to be made.
As described in Section \ref{sec:model_overview}, queueing system \(A\) decides
on a strategy and at the same time, queueing system \(B\) chooses its own 
threshold but unaware of the first queueing system's choice.
Finally, the distributor makes its choice based on the strategies that the 
queueing systems chose to play.

@@

The routing matrix holds the values \((p_A, p_B)\) which are the proportion 
of class 2 individuals to send to queueing system \(A\) and \(B\).
Each pair \((p_A, p_B)\) can be calculated using equation 
(\ref{eq:obj_distributor}) and is essentially
a best response to the actions of the queueing systems.
Thus, using equation \ref{eq:obj_distributor} for all possible sets of 
thresholds we can get the full routing matrix that consists of the proportions
to send to queueing system A (\(p_A\)) and to queueing system B (\(p_B\)).

@@

The game can thus be partitioned into a normal form game between the
two queueing systems and then finding the distributor's best strategy.

@@

In order to populate the payoff matrices and the routing matrix the method
of backwards induction is used.
Consider Figure \ref{fig:imperfect_info_game} and the flow of the game that was
described (i.e. \(Q_A, Q_B \rightarrow D\)).
Due to the fact that the payoff matrices \(A\) and \(B\) depend on the routing 
matrix \(R\) the entries of the matrices are calculated in a backwards way 
(\(D \rightarrow Q_A, Q_B\)). 
Thus for every pair of strategies \(T_A, T_B\), the proportion of individuals 
that are to be transported to each queueing system is calculated first.

Consider a game where the capacities of the two systems are \(N_A = 4\) and 
\(N_B = 3\).
The strategy space of players \(Q_A\) and \(Q_B\) would then be 
\(T_A = \{1, 2, 3, 4\}\) and \(T_B = \{1, 2, 3\}\) respectively.
Now, starting from an arbitrary starting point of \(T_A=1\) and \(T_B=1\), the
corresponding entry of the routing matrix the routing matrix can be calculated.
Using equation (\ref{eq:obj_distributor}) for \(T_A=1\) and \(T_B=1\):
\begin{align}
    & \alpha L_A(p_A;T_A=1;T_B=1) + (1 - \alpha) B_A(p_A;T_A=1;T_B=1) = 
    \nonumber \\
    & \alpha L_B(p_B;T_A=1;T_B=1) + (1 - \alpha) B_B(p_B;T_A=1;T_B=1) 
    \label{eq:obj_distributor_1_1}
\end{align}

@@

These are the utilities of players \(A\) and \(B\) when both players choose a
strategy of \(T = 1\).
Here \(R\) is the predefined waiting time target to be met by a percentage of 
individuals \( \hat{P} \) and \(P(W_i < t)\) is defined in section
\ref{sec:proportion_within_target}.

@@

Another approach to measuring emergent behaviour is to consider 
the emergence itself and not only stable end points. 
Indeed, some Nash equilibria might not arise naturally. 
Thus in order to analyse the strategies played by the two EDs, the learning 
algorithm asymmetric replicator dynamics is 
used~\cite{asymmetricreplicatordynamics}.
The two players are modelled as two separate populations where each 
individual in the population is assigned a strategy.
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each strategy is defined as:

>>>>

The problem defined in section \ref{sec:model_overview} describes a normal-form
game between the decision makers of two hospitals and a third player, the 
ambulance service, that 
decides how to distribute individuals to the systems.
The strategy space of the two hospitals is defined as the possible values
that the threshold parameter can take \(T_i \in [1, N_i]\).
Then, the ambulance service has to decide on the proportion of individuals to 
send to 
each hospital \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
and \(p_A + p_B = 1\).
Figure \ref{fig:imperfect_info_game} 
shows a diagrammatic representation of the game to be played and the decisions 
to be made.
As described in Section \ref{sec:model_overview}, hospital \(A\) decides
on a strategy and at the same time, hospital \(B\) chooses its own 
threshold but unaware of the first hospital's choice.
Finally, the ambulance service makes its choice based on the strategies that the 
hospitals chose to play.

@@

The routing matrix holds the values \((p_A, p_B)\) which are the proportion 
of ambulance patients to send to queueing systems \(A\) and \(B\).
Each pair \((p_A, p_B)\) can be calculated using equation 
(\ref{eq:obj_distributor}) and is essentially
a best response to the actions of the hospitals.
Thus, using equation \ref{eq:obj_distributor} for all possible sets of 
thresholds we can get the full routing matrix that consists of the proportions
to send to hospital A (\(p_A\)) and to hospital B (\(p_B\)).

@@

The game can thus be partitioned into a normal form game between the
two hospitals and then finding the ambulance service's best strategy.

@@

In order to populate the payoff matrices and the routing matrix the method
of backwards induction is used.
Consider Figure \ref{fig:imperfect_info_game} and the flow of the game that was
described (i.e. \(H_A, H_B \rightarrow D\)).
Due to the fact that the payoff matrices \(A\) and \(B\) depend on the routing 
matrix \(R\) the entries of the matrices are calculated in a backwards way 
(\(D \rightarrow H_A, H_B\)). 
Thus for every pair of strategies \(T_A, T_B\), the proportion of individuals 
that are to be transported to each queueing system is calculated first.

Consider a game where the capacities of the two systems are \(N_A = 4\) and 
\(N_B = 3\).
The strategy space of players \(H_A\) and \(H_B\) would then be 
\(T_A = \{1, 2, 3, 4\}\) and \(T_B = \{1, 2, 3\}\) respectively.
Now, starting from an arbitrary starting point of \(T_A=1\) and \(T_B=1\), the
corresponding entry of the routing matrix the routing matrix can be calculated.
Using equation (\ref{eq:obj_distributor}) for \(T_A=1\) and \(T_B=1\):
\begin{align}
    & \alpha L_A(p_A;T_A=1;T_B=1) + (1 - \alpha) B_A(p_A;T_A=1;T_B=1) = 
    \nonumber \\
    & \alpha L_B(p_B;T_A=1;T_B=1) + (1 - \alpha) B_B(p_B;T_A=1;T_B=1) 
    \label{eq:obj_distributor_1_1}
\end{align}

@@

These are the utilities of hospitals \(A\) and \(B\) when both players choose a
strategy of \(T = 1\).
Here \(R\) is the predefined waiting time target to be met by a percentage of 
individuals \( \hat{P} \) and \(P(W_i < t)\) is defined in section
\ref{sec:proportion_within_target}.

@@

Another approach to measuring emergent behaviour is to consider 
the emergence itself and not only stable end points. 
Indeed, some Nash equilibria might not arise naturally. 
Thus in order to analyse the strategies played by the two hospitals, the 
learning 
algorithm asymmetric replicator dynamics is 
used~\cite{asymmetricreplicatordynamics}.
The two hospitals are modelled as two separate populations where each 
individual in the population is assigned a strategy.
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each strategy is defined as:
